STM single case

### 2019-04-04 Messy Code/stm single case.Rmd
creates stm model for catalogues

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("Output/d_text.RDATA")
```

@@

rm(my_cast_dtm)
```

```{r covariates}
#get covariates
covariates <- tribble(
  ~Origin,    ~Data,
  "catalogues", d_text$catalogues %>% distinct(`Course ID`, department),
  "manuals", d_text$manuals %>% mutate(department = "UCM") %>% distinct(`Course ID`, department)
)
```
###STM Corpus
We convert our DTMs into STM corpus to access to full functionality in STM package.
```{r as STM corpus, eval = TRUE}

stm_corpus <- d_cast %>% map(asSTMCorpus)

@@

  STM_model <- stm(corpus$documents, corpus$vocab, K = n_topics, init.type = "Spectral")
}
```
####My_stm_eval Function
This function applied stm but with heldout vocab and documents. 
```{r}
my_stm_eval <- function(heldout, n_topic){
  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
}
```

@@

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup()%>%
    pull(term)%>%
    unique()
}
```
###Model Tibbles
####For use:
```{r models in tibble}
topic_numbers <- seq(from = 5, to = 10, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)

stm_model <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 2) ) %>%
  mutate(
  #Identification information
  Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         
  `Topic ID` = paste(Origin, n_topic, sep = "_"),
  #DTM

  DTM       = pmap(.l = list(Origin), .f = extract_dtm),

  doc_names = map(DTM, rownames),
  #STM Corpus
  Corpus           = pmap(.l = list(Origin),   .f = extract_corpus), 
  #Documents- STM corpus
  Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
  #Vocab- STM corpus
  Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
  #Data- STM corpus
  Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
  #Fit Model
  Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),

@@

```
####TESTING AND INSPECTING MODELS
```{r model inspection}
my_test <-  stm_model %>% filter(n_topic == 10, Origin == "manuals")
```
####For evaluation
```{r models in tibble}
topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)

@@

>>>>

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("/Users/sofia/Documents/DARS/GitDARS/Output/d_text.RDATA")
```

@@

rm(my_cast_dtm)
```
###covariates
```{r covariates}
catalogues_covariates <- d_text$catalogues %>% distinct(`Course ID`, department)
manuals_covariates    <- d_text$manuals %>% mutate(department = "UCM") %>% distinct(`Course ID`, department)
```
###STM Corpus
We convert our DTMs into STM corpus to access to full functionality in STM package.
```{r as STM corpus, eval = TRUE}
catalogues_corpus <- asSTMCorpus(d_cast$catalogues)
manuals_corpus    <- asSTMCorpus(d_cast$manuals)

@@

  STM_model <- stm(corpus$documents, corpus$vocab, data= data, prevalence = ~department, K = n_topics, init.type = "Spectral")
}
```
####My_stm_eval Function
This function applied stm but with heldout vocab and documents. 
```{r}
my_stm_eval <- function(heldout, n_topic){
  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
}
```

@@

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup()%>%
    pull(term)%>%
    unique()
}
```
###Model Tibbles
####For use:
Catalogues:
```{r models_catalogues in tibble}
topic_numbers <- seq(from = 5, to = 10, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)

stm_model <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 1) ) %>%
  mutate(
  #Identification information
  Origin     = rep(c("catalogues"), length(topic_numbers)),         
  `Topic ID` = paste(Origin, n_topic, sep = "_"),
  DTM        = pmap(.l = list(Origin), .f = extract_dtm),
  Model      = map(n_topic, .f = my_stm, catalogues_corpus, catalogues_covariates),

@@

Manuals_ models do not work:
```{r models_manuals in tibble}
topic_numbers <- seq(from = 5, to = 5, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)

stm_model_manuals <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 1) ) %>%
  mutate(
  #Identification information
  Origin     = rep(c("manuals"), length(topic_numbers)),         
  `Topic ID` = paste(Origin, n_topic, sep = "_"),
  DTM        = pmap(.l = list(Origin), .f = extract_dtm),
  Model      = map(n_topic, .f = my_stm, manuals_corpus, manuals_covariates),

)
```

```{r}
topic_model_manual <- 
```
Inspection plots:
```{r plot STM}
select_topic_model <- function(origin, K){
  model <- stm_model %>% 
    filter(Origin == origin, n_topic == K) %>%
    pull(Model)

   model <- model[[1]]
}

test <- select_topic_model("catalogues", 10)

plot.STM(test, "labels", topics = c(6:10))

####For evaluation
```{r models in tibble}
topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)

@@

```{r}
prep <- estimateEffect(1:10 ~ department, test, meta=catalogues_covariates, 
                       uncertainty="Global")
plot(prep, covariate="department", topics=c(3, 5, 10), model=test, 
     method="difference", cov.value1="UCV", cov.value2="UCM",
     main="Effect of UCV vs. UCM")
```
